### 2017-09-05 monograph/thesis/chapters/chapter_1.tex
Reviewed the chapter_1.tex English machine initial translation.

\cleardoublepage
\phantomsection

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
\addcontentsline{toc}{chapter}{\texorpdfstring{\MakeTextUppercase{Capítulo 1}}{Capítulo 1}}

\chapter{Capítulo 1}

\newpage

\section{Introdução}

>>>>

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\cleardoublepage
\phantomsection

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\chooselang{Introduction}{Introdução}}

\chooselang
{
    Questions like ``What are good programming practices?'' Or ``Why are these practices are good?''
    Are not easy to answer. But each programmer learns to write their codes in a certain way, with
    certain features like using 4 or 8 spaces to indent lines, always leave a blank line before each
    control structure as if or for statements, and alike rules. % TODO, put reference for this

    But entering the universe of good practices, there are many things for discoursing. So in this
    work implementation tool called ``Object Beautifier'' specifically dedicates on how to perform
    the best layout/display of programming code on the computer screen, so that maximize and
    facilitate the understanding of same. Therefore, allowing the programmer to disperse more tempe
    thinking about its coding algorithms problem, other than trying to decipher the information that
    is presented to it on the screen through infinit different code layouts. % TODO, put reference for this

    Within this work\textquotesingle s area, we need to also think long and hard about how to share
    the programming code of the programmers among you. Now, the problem of human diversity, like all
    big scientific questions -- how do you explain something like that -- It can be broken down into
    sub-questions. It happens many times, which is a good practice for a `Programmer A', is not the
    same to another `Programmer B'. For example, imagine some code where a programmer decided to put
    before each `if' statement, a blank line. It is therefore expected that whenever we see a blank
    line we can potentially find a matching `if', which can be considered a quite useful pattern
    matching as empty line may call better your attention. % TODO, put reference for this

    But again this is something heavily dependent of what each one learning through their life time.
    Imagine another programmer do not liked this rule, and when he was writing your code involving
    an `if', he did not put such blank line another programmer is expecting. So when the first
    programmer start reading its the code and look for `if', he will be expecting for blank lines
    before its if\textquotesingle s. But will lose some time searching until realize another
    programmer does not put them, or perhaps he forgot to insert them. % TODO, put reference for this

    These differences are due to the diversity of ways we learn programming, i.e., to the ways we
    are used to doing coding, as much as the abilities and objectives of every programmer developed.
    Hence, nowadays it becomes a big problem because we increasingly need more and more programmers
    working together developing several and diverse computing systems. Where the latter is due to
    the fact of the complexity of computer systems growing increasingly, therefore over requiring
    programmers working and sharing their codes and ideas. % TODO, put reference for this

    Moreover besides only worrying about how the code is displayed on their computer screen, we need
    to worry about on how it will be saved in the file system on its `plain-text' mode. Since for
    code sharing, it is vital for you to use a versioning control system which enable project
    manager\textquotesingle s and programmers themselves, take control of their code changes. It does allow to
    easily perform the tracking of code changes and allow you to better understand what each
    programmer is doing every time he formalizes a change in the code through a `commit', as in
    `git' systems for example. % TODO, put reference for this

    That is because while working with a versioning system like `git', we need to keep the code
    among a single style or which we may call a `good practice' set as standard for everybody, due
    the fact of letting each programmer to write as he pleases, there will be plenty of noise on the
    code review and we are figuring out what actually each programmer did. Hence, if every
    programmer re-writes the history making changes like inserting new lines before each if, we end
    up with too much noise and focus of a versioning system is to look at only those changes that
    are significant to the code, such as the creation of new functions and not the addition of new
    blank lines (ref find\_some). % TODO, put reference for this (ref coding\_horror)

    Talking about the last thing pointed out, we could also think about an approach to creating a
    new version control system which focuses only on significant changes to the code, while
    reviewing code changes. However, this approach could not be ideal, as for example, it would
    allow programmers to start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code re-adding new lines before
    each one of your beloved if\textquotesingle s, just because some night shift programmer had just
    removed them? % TODO, put reference for this

    \section{Goals}

    Establish relationships between good programming practices and efficiency in programming, in
    addition to a new tool to support programmers in order to automate the long and diverse
    programming process in teams of developers with different programming `best practices'.

    \subsection{Specific Goals}

    \begin{enumerate}
        \item A study on universal programming tools, which from a single software, to work well
        behaved accross all programming languages. Moreover, explain the differences for other
        softwares and the beneficits of a unique tool, instead of several heavly different ones.

        \item Define, determine and classify which one are good programming practices and perform an
        in-depth study on the good practices on visual layout area, also known as code `Beautifying'.

        \item A study on the variety of existing tools for the support of good programming
        practices, beyond a comparative analysis between them, determining their weaknesses and
        strengths.

        \item The definition of a flow pattern of development allowing teams of developers with
        different programming best practices, to work without intervene with each other up to start
        wars of `best good practices'.

        \item Propose a unique tool that allowing several and distinct programming `best practices'
        being implemented in several programming languages, which can be configured and set
        accordindgly to their whishes.
    \end{enumerate}

    \section{Search Method}

    The work will be based on research in articles, books, theses, dissertations, trusted authors
    websites, and through new demonstrated evidences based on arguments in the monograph evolution
    road. Also, present results after building a new tool which proposes a solution for the problems
    presented and detailed.

    In this proposal last chapter which lies in the topic \autoref{sec:implementation}, there is a
    series of weblinks and references preselected and may be used in the release build of this work.
    Noticing the texts of the last section probably will end up gradually moved to the first section
    of the text where there is the theoretical research, while correlated research are incorporated
    in the main written work.

    Moreover, at the end of the first part of this work, the completion of the subject entitled of
    Course Conclusion Work 1, leaving only the information for the implementation of the proposed
    tool to be implemented in the second part of this named thesis on \nameref{sec:implementation}.
}
{ % Portuguese
